Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-18 analysis/normalized.Rmd
Carrying on on values passed to eval

We compute the sites which are at least one given a `V` minimized expression. Then we look at whether they are passed teh default envir or not, and if there are variables in

```{r}
minimized_sites <- E_cano %>% semi_join(val_exprs, by="src_ref") %>% group_by(src_ref) %>% 
  summarize(has_envir = any(!is.na(envir)), has_var = any(has_var, na.rm = TRUE))

@@

>>>>

We compute the sites which are at least one given a `V` minimized expression. Then we look at whether they are passed the default envir or not, and if there are variables in

```{r}
minimized_sites <- E_cano %>% semi_join(val_exprs, by="src_ref") %>% group_by(src_ref) %>% 
  summarize(has_envir = all(!is.na(envir)), has_var = any(has_var, na.rm = TRUE))

@@

r("non default envir value percent", ratio(nrow(non_default_envir), nrow(minimized_sites)))
r("non default envir with var percent", ratio(nrow(non_default_with_var), nrow(non_default_envir)))
```

### 2021-03-18 paper/main.tex
Carrying on on values passed to eval

\paragraph{Variables.}
The most common minimized expression is a variable.\footnote{An arithmetic with some variables and constant will also be normalized to \c{X}, i.e. a variable.} It happens in \packageMinimizedpropsitesa of the sites and is widespread across packages as it is found in \packageMinimizedpackagea packages across our CRAN corpus. The \c{envir} argument is explicitly passed in \packageMinimizedpercentenvira\% of the call sites, which suggests that \eval is used here to get the value of the variable in a non-local environment.

@@

\paragraph{Value.}
Many sites evaluates to \c{V}.  \packageValOneNodePercent of those sites are only passed an expression with one node, \ie one value, not a more complex expression that is later constant folded. \c{V} corresponds to two main categories of expressions passed to \eval:

\begin{itemize}
	\item \eval is passed an actual value, a double, an integer, an environment, a closure and so on
	\item \eval is passed a language expression that trivially evaluates to a value, for instance, \c{quote(1)}, \quote{c("a", "b", "c")}, and does not include variables, so does not depend on a specific environment.
\end{itemize}

For the first category, \eval is not necessary. In \packageNbCallSitesUniqueActualValue sites, \ie \packageCallSitesUniqueActualValuePercent\% sites, it is only passed such actual values. The median number of runs for those sites is \packageMedianRunSitesUniqueActualValue, suggesting it happens because there are rarely triggered in our dataset and all paths are not taken.

The percentage of non default environment passed to \eval is \packageMinimizedpercentenvirc. Some sites are passed both a value or a symbol, which explains that a specific environment is precised.

%TODO: find out the percentage of non-default envir for sites which have both a value and a variable
%TODO: find the same percentage for sites which have at least one variable passed to them?

When a function is evaluated on some variable (\c{F(X)}), the percentage of non default environment is high, \packageMinimizedpercentenvird\%.

\c{FUN} represents a function definition. It entails very few steps of the interpreter, as the body of the new function is just stored for later execution.

\c{\{BLOCK\}} is a sequence of statements. It is usually large, with in average \packageMinimizedoperationsjRnd operations in it.

>>>>

\paragraph{Variables.}
The most common minimized expression is a variable.\footnote{An arithmetic expression with some variables and constant will also be normalized to \c{X}, i.e. a variable.} It happens in \packageMinimizedpropsitesa of the sites and is widespread across packages as it is found in \packageMinimizedpackagea packages across our CRAN corpus. The \c{envir} argument is explicitly passed in \packageMinimizedpercentenvira\% of the call sites, which suggests that \eval is used here to get the value of the variable in a non-local environment.

Similarly, when a function is evaluated on some variable (\c{F(X)}), the percentage of non default environment is high, \packageMinimizedpercentenvird\%.

@@

\paragraph{Values.}
Many sites evaluates to \c{V}.  \packageValOneNodePercent of those sites are only passed an expression with one node, \ie one value, not a more complex expression that is later constant folded. \c{V} corresponds to two main categories of expressions passed to \eval:

\begin{itemize}
	\item \eval is passed an actual value, a double, an integer, an environment, a closure and other simple types,
	\item \eval is passed a language expression that trivially evaluates to a value, for instance, \c{quote(1)}, \c{quote(1 + 1)}, \quote{c("a", "b", "c")}, and does not include variables, so does not depend on a specific environment.
\end{itemize}

For the first category, \eval is not necessary. In \packageNbCallSitesUniqueActualValue sites exhibiting \c{V}, \ie \packageCallSitesUniqueActualValuePercent\% sites, it is only passed such actual values. The median number of runs for those sites is \packageMedianRunSitesUniqueActualValue (average \packageAverageRunSitesUniqueActualValue, standard deviation \packageSdRunSitesUniqueActualValue), suggesting it happens because there are rarely triggered in our dataset and all paths are not taken. However, manual inspection of the source code of some examples shows that some sites actually pass values. For instance, in package \emph{ctmle}, in function \c{evaluate\_candidate\_glmnet}:

\begin{lstlisting}
f1 <- eval(paste("A ~ ", paste(paste(names(X[,-1]), sep=''), collapse=" + ")))
f2 <- as.formula(f1)
\end{lstlisting}

\c{paste} concatenates strings and \eval will just return that string. \c{as.formula} can take a string and convert it to a formula; \eval is not needed here.

The percentage of non default environment passed to \eval is \packageMinimizedpercentenvirc when the minimized expression is a value. Some sites which are passed a value, are also passed different minimized expressions. For those ones, \packageNonDefaultEnvirValuePercent use a non-default environment, and among the one that use a non-default environment, \packageNonDefaultEnvirWithVarPercent have at least one minimized expression with a variable inside.

\paragraph{Function definition.} \c{FUN} represents a function definition. It entails very few steps of the interpreter, as the body of the new function is just stored for later execution.

\paragraph{Sequence of statements.} \c{\{BLOCK\}} is a sequence of statements. It is usually large, with in average \packageMinimizedoperationsjRnd operations in it.
